---
title: "Homework 1"
author: "Astha Gupta 5:45 pm Thursday_Class"
date: "2/7/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{ r }
# Setting the working directory

setwd("/Users/mountainlion/Desktop/2nd Semester/Regression")
getwd() 
```

##Question 1
```{r, echo=TRUE}
# Load the data
y <- read.table("/Users/mountainlion/Desktop/2nd Semester/Regression/HW1/Sporting.csv", header=TRUE, sep=",", stringsAsFactors=FALSE)
head(y)
#tail(y)
print("Summary Statistics")
summary(y)
```
# Univariate Summary

```{r}
# histogram for Age
hist(y$Age, las=TRUE, main="Histogram of Age",
     col="blue", xlab="Age (years)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	

# Histogram for College
hist(y$College, las=TRUE, main="Histogram of College",
     col="cadetblue", xlab="College (percentage)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	

# histogram for HS
hist(y$HS, las=TRUE, main="Histogram of HS",
     col="green", xlab="HS (percentage)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	

# histogram for Income
hist(y$Income, las=TRUE, main="Histogram of Income",
     col="Yellow", xlab="Income(dollars)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	

# histogram for Growth
hist(y$Growth, las=TRUE, main="Histogram of Growth",col="light Yellow", xlab="Growth(percentage/year)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	

# histogram for Sales
hist(y$Sales, las=TRUE, main="Histogram of Sales",
     col="light green", xlab="Sales(Dollar)", cex.lab=2, cex.axis=1.8, cex.main=1.8)
legend("topright", legend="roughly symmetric", bty="n", col="white", border="white", cex=1.5)	
```

## Summary Statistics TAble



## Question 3

# Compute the corelation cofficient r
```{r}

# Scatter plot of Sales vs Age
plot(y$Sales, y$Age, las=TRUE, pch=1, xlab="Age of Customer base (years)", ylab="Sales (dollars)",
     main="Sales versus Age", cex.lab=2, cex.axis=1.8, cex.main=1.8)
# add a bit of noise to each point
plot(jitter(y$Sales), jitter(y$Age), las=TRUE, pch=1, xlab="Age of Customer base (years)", ylab="Sales(dollars)", main="A.Sales versus Age", cex.lab=2, cex.axis=1.8, 
     cex.main=1.8)
mtext("(jittered points)", side=1, line=5)

# Scatter plot of Sales vs percentage of customer base with College diploma

plot(y$Sales, y$College, las=TRUE, pch=1, xlab="Percentage of customer base with a college diploma (percentage)", ylab="Sales (dollars)",main="Sales versus college diploma", cex.lab=2, cex.axis=1.8, cex.main=1.8)
# add a bit of noise to each point
plot(jitter(y$Sales), jitter(y$College), las=TRUE, pch=1, xlab="Percentage of customer base with a college diploma(percentage)", ylab="Sales(dollars)",main="Sales versus college diploma", cex.lab=2, cex.axis=1.8, 
     cex.main=1.8)
mtext("(jittered points)", side=1, line=5)

# Scatter plot of Sales vs Income

plot(y$Sales, y$Income, las=TRUE, pch=1, xlab="Income of customer base (Dollars)", ylab="Sales (dollars)",
     main="Sales versus Income", cex.lab=2, cex.axis=1.8, cex.main=1.8)
# add a bit of noise to each point
plot(jitter(y$Sales), jitter(y$Income), las=TRUE, pch=1, xlab="Income of customer base (years)", ylab="Sales(dollars)",main="Sales versus Income", cex.lab=2, cex.axis=1.8, cex.main=1.8)
mtext("(jittered points)", side=1, line=5)

# Scatter plot of Sales vs HS
plot(y$Sales, y$HS, las=TRUE, pch=1, xlab="Percentage of customer base with a high school diploma(Percentage)", ylab="Sales (dollars)",main="Sales versus HS", cex.lab=2, cex.axis=1.8, cex.main=1.8)
# add a bit of noise to each point
plot(jitter(y$Sales), jitter(y$HS), las=TRUE, pch=1, xlab="Percentage of customer base with a high school diploma(Percentage)", ylab="Sales(dollars)",main="Sales versus HS", cex.lab=2, cex.axis=1.8, cex.main=1.8)
mtext("(jittered points)", side=1, line=5)

# Scatter plot of Sales vs Growth

plot(y$Sales, y$Growth, las=TRUE, pch=1, xlab="Annual population growth rate of customer base over the past 10 years (Percentage/year)", ylab="Sales (dollars)",main="Sales versus Growth", cex.lab=2, cex.axis=1.8, cex.main=1.8)
# add a bit of noise to each point
plot(jitter(y$Sales), jitter(y$Growth), las=TRUE, pch=1, xlab="Annual population growth rate of customer base over the past 10 years (Percentage/year)", ylab="Sales(dollars)",main="Sales versus Growth", cex.lab=2, cex.axis=1.8, cex.main=1.8)

# Compute Corelation
any(is.na(y$Sales))
any(is.na(y$Age))
any(is.na(y$College))
any(is.na(y$Income))
any(is.na(y$HS))
any(is.na(y$Growth))
round(cor(y$Sales, y$Age), digits=4)
round(cor(y$Sales, y$College), digits=4)
round(cor(y$Sales, y$Income), digits = 4)
round(cor(y$Sales, y$HS), digits=4)
round(cor(y$Sales, y$Growth), digits=4)
```
## Question 4

Based on the analysis, College Diploma is the best explanatory variable.
Reason:
## Question 6:
Fitting a linear model, we want to include the summary output:
```{r}
lm.y <- lm(Sales ~ Income, data=y)
summary(lm.y)
```
The formula for fitted model:
$\hat y  =\hat\beta_0 + \hat\beta_1 x$
 
The estimted slope and y-intercept in the equation :
```{r}
library(knitr)

kable(coefficients(summary(lm(Sales ~ College, data=y))))
names(lm.y)
# To plot the regression Line and actual line
par(mar=c(5.1, 4.1, 4.1, 2.1), mgp=c(3, 1, 0))
plot(y$Income, y$Sales, las=TRUE, pch=19, col="#99000070", 
	xlab=" Income of customer base(dollars)", ylab="Sales (dollars)",
	main="Sales versus Income", cex.lab=1, cex.axis=1, cex.main=1)
abline(a=0, b=1, col="firebrick", lwd=3)
abline(coefficients(lm.y), col="forestgreen", lwd=3)
legend("bottomright", legend="y=x", col="firebrick", lwd=3, bty="n", cex=1.5)

#from summary(), see Multiple R-Squared
summary(lm.y) 

#simple linear regression, square correlation r:
round(cor(y$Sales, y$Income)^2, digits = 4)

#Fitting a Linear Model Using Summary Statistics
#slope: beta_1 = r*sy/sx
cor(y$Sales, y$Income)*sd(y$Sales)/sd(y$Income)
# y-intercept: mean.y - slope*mean.x
## check this (mean(y$Income) - beta.1*mean(y$Sales))
range(y$Income)



```